Turbulence in giant extragalactic HII regions

### 2021-03-30 mnras_template.tex
Javier changes 27–30 March

%We have used longslit spectroscopy observations obtained with the William Herschel Telescope with the aim of characterizing the turbulent state of the ionized gas in giant HII regions.
%For this purpose, the \halpha, \n, \oi\ and \s\ emission lines were investigated applying a statistical analysis on their velocities samples. 
%The correlations in our results are evidence that the velocity field can be consider as homogeneous turbulence, a statistically stationary process. This turbulent motions can be described by a power law with a mean index of 0.60$\pm$0.02 and a physical coherent scale up to $\sim$60 pc for NGC 604 and 1.04$\pm$0.01 with a correlation length up to $\sim$60 pc for NGC 595. 
%The physical interpretation of our results consider that an energy cascade is taking place for all the ionic species.
%Finally, we give our explanation for our results and fit them in the context of turbulence in giant HII regions.

\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
HII regions -- ISM: individual object: NGC 604 -- ISM: kinematics and dynamics -- techniques: spectroscopic -- turbulence
\end{keywords}

@@

There is evidence that different phases of the interstellar medium exhibits a chaotic behavior \citep{franco1999interstellar,elmegreen2004interstellar,scalo2004interstellar}. Velocity fields shows complex motions in the plane-of-sky (POS) and a non-thermal broadening on their spectral lines, suggests disorder motions along the line-of-sight (LOS). The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{chepurnov2010extending}, is closely related to the existence of turbulent flows. The high Reynolds numbers (Re), in the order of 10$^{4}$ and 10$^{9}$, present in these objects \citep{lagrois2011} is taken as first approach to understand the relationship between turbulence and the observed movements. Despite numerous attempts in characterizing the turbulence in the photoionized gas, little understood on how the results indicate something about the physics of the object.

The mathematical techniques developed by \citet{kolm1,heisenberg1951stability} were first applied to astronomical observations by \citet{von1951methode} and \citet{munch1958internal}. Their aim was to investigate the projection of a three-dimensional function into the plane of the sky. This procedure using the structure function allowed to determine a distinction between homogeneous turbulence and pure random velocity fluctuations, in this case in the galactic HII region, the Orion Nebula. The analysis on the turbulence of the Orion Nebula was continued by \citet{castaneda1987} and \citet{1992ApJ...387..229O}. In more recent years \cite{medina2014} and \cite{arthur2016turbulence} used another statistical technique called velocity channel analysis (VCA) \citep{2000ApJ...537..720L}, along the structure function, to study the Orion nebula. Recently, the structure function was used with full 6D measurements (position-velocity) to study the motions of stars in the Orion Molecular Cloud Complex. \cite{2021ApJ...907L..40H} argue that newborn stars should reflect the turbulent kinematics of their natal clouds. Using this previous method they are free of the projected element that interfere with previous gas-based studies and their results agree with the scaling law proposed by \cite{1981MNRAS.194..809L}.

The first attempt at characterizing turbulence in a giant extragalactic HII region (GEHR) was done by \citet{1961MNRAS.122....1F} with the 30 Dor complex in the LMC, finding no indication of turbulent motions. \cite{2019arXiv191203543M} investigated the structure function in 30 Dor finding on their results that the structure function is entirely flat on scales from 3 to 200 pc. Also, \cite{2019arXiv191203543M} studied the motions in NGC 604, previously analyzed by \cite{tanco1997}. Both results shows that there is a two slope behavior for the structure function. The structure function in the GEHR NGC 595 was first obtained by \cite{lagrois2009multi} and the analysis was expanded by \cite{lagrois2011}. In all previous studies the Kolmogorov law does not apply to any result.

@@

\citet{smith1970} discovered that the line width of GEHRs was supersonic, of the order of $\sigma \sim$ 17-26 km s\kms. \citet{melnick1977,terlevich1981} have shown an empirical relationship between the line width and the integrated properties of the HII regions as the diameter or the luminosity ($R \sim \sigma ^{\sim 2}$ ; $L \sim \sigma ^{\sim 4}$). They conclude that GEHR  follow this relations as self-gravity systems like globular clusters or elliptical galaxies. The idea of a virial system has been developed by \citet{1993ApJ...418..767T,munoz1996} into the \textit{Cometary Stirring Model} (CSM) with the aim to separate the mechanism that contribute to the line broadening. The stellar winds also tend to be used for an explanation of the line broadening and turbulence in GEHRs \citep{1994ApJ...425..720C}. This features seems to drive visually the regions with filaments, arcs and shells. On their spectra double and multiple emission features are signature of these objects. \cite{2020MNRAS.494...97S} argue that winds on ionizing clusters in GEHR must merge into a hot cluster because of the close proximity of the massive stars. \cite{2019ApJ...871...17U} propose that stellar feedback is an important source of energy to maintain turbulence in nearby galaxies.

@@

\citet{2000PASP..112.1138M} and \citep{maiz2004} provides details of the observational setup for the the ISIS instrument. In summary, the spectra were obtained (1998 18-19 August) using a position angle of 90$^{\circ}$ and the slit width was 1". Two different spectra were taken simultaneously for each position: one for the red arm, between 6390 and 6849 \r{A} and another on the blue arm between 4665 and 5065 \r{A}. The slit had a length of 200" and ten  positions  were observe with an exposure time ranging from 900 to 1200 s for every slit. The  data we used was reduced again by \citet{jen2013} using the IRAF \citep{1999ascl.soft11002N} astronomical software. The ISIS observations were used by \citet{TT2000} and \citet{maiz2004}.

@@

Figure \ref{fig:M604} shows the two-dimensional radial velocity map of NGC 604 in H$\alpha$. ISIS observations have been limited with the aim to match the zone cover by TAURUS instrument. The velocity scale on both instruments reflects the radial velocity in the reference frame of the region taking as a  reference point the most luminous pixel. This pixels has a value of -253.11 km/s. Figure \ref{fig:M595} shows the two-dimensional radial velocity map of NGC 595 in H$\alpha$.

@@

\subsection{NGC 604}

@@

\subsection{NGC 595}

Figure \ref{fig:SF595} shows the structure function of NGC 595 for the H$\alpha$ emission line for the TAURUS instruments. The $m_{2D}$ is 1.7 with a correlation length of 11 pc. The $\sigma$ is 6.6 km/s. In this case it is possible to fit values under 4 pc, but this small scale region is affected due to the seeing. The range of scale for this regions stays between 10 and 11 pc as in NGC 604. The values of the structure function rise until 30 pc. Scales larger than this shows a random around 2$\sigma$.

@@

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/HV}
\caption{Hubble V second-order structure functions for H$\alpha$ emission line for TAURUS instrument.}
\label{fig:SFV}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/HX}
\caption{Hubble X second-order structure functions for H$\alpha$ emission line for TAURUS instrument.}
\label{fig:SFX}
\end{figure}

@@

In an idealized case, at scales larger than r$_{0}$ the structure function flattens as it tends towards the asymptotic value of 2$\sigma$ \citep{arthur2016turbulence}. Figure \ref{fig:SF604} shows that the structure functions, except for \cite{2019arXiv191203543M}, follow a periodic behavior around 2$\sigma$. Using as reference the TAURUS results, the wave starts at 35 pc with a series of $ >$2$\sigma$ values up to $\sim$100 pc. Then $<$2$\sigma$ values follow until the largest scales of 150 pc. Therefore this periodic behavior is related to scales of 100 pc across our sample box.

@@

\section{Conclusions}\label{sec:disc}

>>>>

We used the radial velocity field in H$\alpha$ emission with the aim of characterizing the turbulent state of the ionized gas in giant HII regions. For this purpose we use long-slit spectroscopy and Fabry-Perot observations obtained with the William Herschel Telescope. Each velocity sample was investigated applying the second order structure function. The correlations in our results are evidence that the velocity field can be consider in a turbulent state. This turbulent motions are described by a power-law with a mean index of 1.7. The physical interpretation of the power-law behavior consider that an energy cascade is taking place in the photoionized gas.
\end{abstract}

% Select between one and six entries from the list of approved keywords.
% Don't make up new ones.
\begin{keywords}
HII regions -- ISM
\end{keywords}

@@

Different phases of the interstellar medium exhibits a chaotic behavior \citep{franco1999interstellar,elmegreen2004interstellar,scalo2004interstellar}. Velocity fields shows complex motions in the plane-of-sky (POS), and a non-thermal broadening on their spectral lines suggests disorder motions along the line-of-sight (LOS). The large lengths of astrophysical objects, ranging in scales from 10$^{6}$ to 10$^{17}$ m \citep{chepurnov2010extending}, and the high Reynolds numbers (Re), in the order of 10$^{4}$ and 10$^{9}$, of these objects \citep{lagrois2011} is related to the existence of turbulent flows. Despite numerous attempts in characterizing the turbulence in the photoionized gas, little understood on how the results indicate something about the physics of the object.

The mathematical techniques developed by \citet{kolm1,heisenberg1951stability} were first applied to astronomical observations by \citet{von1951methode} and \citet{munch1958internal}. Their aim was to investigate the projection of a three-dimensional function into the plane of the sky. This procedure using the structure function allowed to determine a distinction between homogeneous turbulence and pure random velocity fluctuations, for the galactic HII region, the Orion Nebula. The analysis on the turbulence of the Orion Nebula was continued by \citet{castaneda1988} and \citet{1992ApJ...387..229O}. In more recent years \cite{medina2014} and \cite{arthur2016turbulence} used another statistical technique called velocity channel analysis (VCA) \citep{2000ApJ...537..720L}, along the structure function to study the same region. Recently, the structure function was used with full 6D measurements (position-velocity) to study the motions of stars in the Orion Molecular Cloud Complex. \cite{2021ApJ...907L..40H} argue that newborn stars should reflect the turbulent kinematics of their natal clouds. Using this previous method they are free of the projected element that interfere with previous gas-based studies and their results agree with the scaling law proposed by \cite{1981MNRAS.194..809L}.

The first attempt at characterizing turbulence in a giant extragalactic HII region (GEHR) was done by \citet{1961MNRAS.122....1F} with the 30 Dor complex in the LMC, finding no indication of turbulent motions. \cite{2019arXiv191203543M} investigated the structure function in 30 Dor finding on their results that the structure function is entirely flat on scales from 3 to 200 pc. Also, \cite{2019arXiv191203543M} studied the motions in NGC 604, a GEHR previously analyzed by \cite{tanco1997}. Both results shows that there is a two slope behavior for the structure function. The structure function in the GEHR NGC 595 was first obtained by \cite{lagrois2009multi} and the analysis was expanded by \cite{lagrois2011}. In all previous studies the Kolmogorov law does not apply to any result.

@@

\citet{smith1970} discovered that the line width of GEHRs was supersonic, of the order of $\sigma \sim$ 17-26 km s\kms. \citet{melnick1977,terlevich1981} have shown an empirical relationship between the line width and the integrated properties of the HII regions as the diameter or the luminosity ($R \sim \sigma ^{\sim 2}$ ; $L \sim \sigma ^{\sim 4}$). Correlations between kinematics and physical properties of GEHR have been common tools to study this excess. They conclude that GEHRs follow this relations as self-gravity systems like globular clusters or elliptical galaxies. The idea of a virial system has been developed by \citet{1993ApJ...418..767T,munoz1996} into the \textit{Cometary Stirring Model} (CSM) with the aim to separate the mechanism that contribute to the line broadening. The stellar winds also tend to be used for an explanation of the line broadening and turbulence in GEHRs \citep{1994ApJ...425..720C}. This features seems to drive visually the regions with filaments, arcs and shells. On their spectra double and multiple emission features are signature of these objects. \cite{2020MNRAS.494...97S} argue that winds on ionizing clusters in GEHR must merge into a hot cluster because of the close proximity of the massive stars. \cite{2019ApJ...871...17U} propose that stellar feedback is an important source of energy to maintain turbulence in nearby galaxies.

@@

\citet{2000PASP..112.1138M} and \citep{maiz2004} provides details of the observational setup for the the ISIS instrument (1998 18-19 August). In summary, the spectra were obtained  using a position angle of 90$^{\circ}$ and the slit width was 1". Two different spectra were taken simultaneously for each position: one for the red arm, between 6390 and 6849 \r{A} and another on the blue arm between 4665 and 5065 \r{A}. The slit had a length of 200" and ten  positions  were observe with an exposure time ranging from 900 to 1200 s for every slit. The  data we used was reduced again by \citet{jen2013} using the IRAF \citep{1999ascl.soft11002N} astronomical software. The ISIS observations were used by \citet{TT2000} and \citet{maiz2004}.

@@

Figure \ref{fig:M604} shows the two-dimensional radial velocity map of NGC 604 in H$\alpha$. ISIS observations have been limited with the aim to match the zone cover by TAURUS instrument. The velocity scale on both instruments reflects the radial velocity in the reference frame of the region taking as a  reference point the most luminous pixel. This pixels has a value of -253.11 km/s. Figure \ref{fig:M595} and \ref{fig:MHub} shows the two-dimensional radial velocity map in H$\alpha$ of NGC 595, Hubble V and Hubble X, respectively.

@@

@@

Figure \ref{fig:SF595} shows the structure function of NGC 595 for the H$\alpha$ emission line. The $m_{2D}$ is 1.7 with a correlation length of 11 pc. The $\sigma$ is 6.6 km/s. In this case it is possible to fit values under 4 pc, but this small scale region is affected due to the seeing. The range of scale for this regions stays between 10 and 11 pc as in NGC 604. The values of the structure function rise until 30 pc. Scales larger than this shows a random pattern around 2$\sigma$.

Figure \ref{fig:SFV} shows the structure function of Hubble V for the H$\alpha$ emission line. The $m_{2D}$ is 1.8 with a correlation length of 4 pc and a $\sigma$ of 2.8 km/s. The structure function values keep going up and reach a maximum at $\sim$28 pc, above this value there is no clear pattern.

Figure \ref{fig:SFX} shows the structure function of Hubble V for the H$\alpha$ emission line. The $m_{2D}$ is 1.7 with a correlation length of 4 pc. The $\sigma$ of the region is 3.6 km/s. For this region, the structure functions keeps its tendency of going up to a scale o $\sim$ 18 pc.

@@

\begin{figure}
\centering 
\includegraphics[width=2.5in]{Figures/HV}
\caption{Hubble V second-order structure functions for H$\alpha$ emission line for TAURUS instrument.}
\label{fig:SFV}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=2.5in]{Figures/HX}
\caption{Hubble X second-order structure functions for H$\alpha$ emission line for TAURUS instrument.}
\label{fig:SFX}
\end{figure}

@@

In an idealized case, at scales larger than r$_{0}$ the structure function flattens as it tends towards the asymptotic value of 2$\sigma$ \citep{arthur2016turbulence}. Figure \ref{fig:SF604} shows that the structure functions, except for \cite{2019arXiv191203543M}, follow a periodic behavior around 2$\sigma$. Using as reference the TAURUS results, the wave starts at 35 pc with a series of $ >$2$\sigma$ values up to $\sim$100 pc. Then $<$2$\sigma$ values follow until the largest scales of 150 pc. Therefore this periodic behavior is related to scales of $\sim$100 pc across our sample box.

@@

\section{Conclusions}\label{sec:concl}
